---
title: "DEseq2 -- Analysis Expression Proliferation Correlation Expression"
output:
  pdf_document: default
  html_document: default
---

```{r, include = FALSE}
library(SummarizedExperiment)
library(DESeq2)
library(ggplot2)
library(limma)
```

We want to add a new rowData item in our Summarized Experiment objects. To do it we import the previous object and we build a new one using the old (previous .rds) and new one. In this case we will add Gene Name data. Gene Name data is the ENS_id of each gene but without the last 3 characters. It's important to have gene names in this format for further operations that will be carried out later on. 
(In this specific case we would only need to modify rowData, but I'll build all three items (assays, rowData and colData), to exemplify it completely)

```{r}
#FIB
FIBobj <- readRDS("FIB.rds")
Gene_name <- substr(rowData(FIBobj)$ENS_id, 1, 18)
NewFIBRowData <- data.frame(rowData(FIBobj), Gene_name, row.names = rownames(FIBobj))
FIBobj1 <- SummarizedExperiment(assays = list(counts = assays(FIBobj)$counts))
rowData(FIBobj1) <- NewFIBRowData
colData(FIBobj1) <- colData(FIBobj)
FIBobj1

#ESC
ESCobj <- readRDS("ESCobj.rds")
Gene_name <- substr(rowData(ESCobj)$ENS_id, 1, 18) #Not really necessary because both objects have the same gene names in the same order, but just in case.
NewESCRowData <- data.frame(rowData(ESCobj), Gene_name, row.names = rownames(ESCobj))
ESCobj1 <- SummarizedExperiment(assays = list(counts = assays(ESCobj)$counts))
rowData(ESCobj1) <- NewESCRowData
colData(ESCobj1) <- colData(ESCobj)
ESCobj1

```

We will save it and from now on, use it (more practical). 

```{r}
saveRDS(object = ESCobj1, file = "ESCobj1.rds")
saveRDS(object = FIBobj1, file = "FIBobj1.rds")
```

#Yeast object (w/data from van Dijk paper)

```{r}
YeastTab <- read.table("FitFlowRNAseq.tab.tsv", header = TRUE)
AssaysYeast <- cbind(YeastTab$SlowFPKM, YeastTab$FastFPKM)
YeastObj <- SummarizedExperiment(assays=list(counts=AssaysYeast))
TranscriptName <- YeastTab$TranscriptID
rowData(YeastObj) <- TranscriptName
rownames(YeastObj) <- TranscriptName
colnames(YeastObj) <- c("SlowFPKM", "FastFPKM")
columnDataYeast <- DataFrame(ProliferationState=c("Slow FPKM", "Fast FPKM"))
colData(YeastObj) <- columnDataYeast
saveRDS(file = "Yeast_vanDijk.rds", object = YeastObj)
```

-------------------------------------------------------------------------------------------------------------------------

Read the files

```{r}
ESCobj1 <- readRDS(file = "ESCobj1.rds")
FIBobj1 <- readRDS(file = "FIBobj1.rds")
YeastObj1 <- readRDS(file = "Yeast_vanDijk.rds")
```

**Distribution of expression levels across genes**

Before any filtering, only changed 0 for 0.001

```{r}
assays(ESCobj1)$counts[assays(ESCobj1)$counts < 0.001] <- 0.001
ESCobj1 <- ESCobj1[rowData(ESCobj1)$CoincBehavClass != "TPM CIs Zero", ]
assays(FIBobj1)$counts[assays(FIBobj1)$counts < 0.001] <- 0.001
FIBobj1 <- FIBobj1[rowData(FIBobj1)$CoincBehavClass != "TPM CIs Zero", ]

#FIB
Slow_MeanFIB <- rowMeans(log2(assays(FIBobj1)$counts[, c(1, 4)]))
Proliferation <- "SlowFIB"
Slow_MeanFIB <- data.frame(Slow_MeanFIB, Proliferation)
colnames(Slow_MeanFIB) <- c("MeanExpression", "Proliferation")
Medium_MeanFIB <- rowMeans(log2(assays(FIBobj1)$counts[, c(2, 5)]))
Proliferation <- "MediumFIB"
Medium_MeanFIB <- data.frame(Medium_MeanFIB, Proliferation)
colnames(Medium_MeanFIB) <- c("MeanExpression", "Proliferation")
Fast_MeanFIB <- rowMeans(log2(assays(FIBobj1)$counts[, c(3, 6)]))
Proliferation <- "FastFIB"
Fast_MeanFIB <- data.frame(Fast_MeanFIB, Proliferation)
colnames(Fast_MeanFIB) <- c("MeanExpression", "Proliferation")
FIBdf <- rbind(Slow_MeanFIB, Medium_MeanFIB, Fast_MeanFIB)
colnames(FIBdf) <- c("MeanExpression", "Proliferation")
FIBdf <- data.frame(FIBdf)
plot_explevelsFIB <- ggplot(FIBdf, aes(x = FIBdf[, 1], group = FIBdf[, 2], color = FIBdf[, 2])) + geom_density()
plot_explevelsFIB <- plot_explevelsFIB + xlab("Mean Expression (log2CPM)") + theme_bw() + theme(legend.title = element_blank())

#ESC
Slow_MeanESC <- rowMeans(log2(assays(ESCobj1)$counts[, c(1, 4)]))
Proliferation <- "SlowESC"
Slow_MeanESC <- data.frame(Slow_MeanESC, Proliferation)
colnames(Slow_MeanESC) <- c("MeanExpression", "Proliferation")
Medium_MeanESC <- rowMeans(log2(assays(ESCobj1)$counts[, c(2, 5)]))
Proliferation <- "MediumESC"
Medium_MeanESC <- data.frame(Medium_MeanESC, Proliferation)
colnames(Medium_MeanESC) <- c("MeanExpression", "Proliferation")
Fast_MeanESC <- rowMeans(log2(assays(ESCobj1)$counts[, c(3, 6)]))
Proliferation <- "FastESC"
Fast_MeanESC <- data.frame(Fast_MeanESC, Proliferation)
colnames(Fast_MeanESC) <- c("MeanExpression", "Proliferation")
ESCdf <- rbind(Slow_MeanESC, Medium_MeanESC, Fast_MeanESC)
colnames(ESCdf) <- c("MeanExpression", "Proliferation")
ESCdf <- data.frame(ESCdf)
plot_explevelsESC <- ggplot(ESCdf, aes(x = ESCdf[, 1], group = ESCdf[, 2], color = ESCdf[, 2])) + geom_density()
plot_explevelsESC <- plot_explevelsESC + xlab("Mean Expression (log2CPM)") + theme_bw() + theme(legend.title = element_blank())
```


```{r}

#ESC

Proliferation <- "SlowESC1"
Slow_MeanESC1 <- data.frame(log2(assays(ESCobj1)$counts[, 1]), Proliferation)
colnames(Slow_MeanESC1) <- c("MeanExpression", "Proliferation")
Proliferation <- "SlowESC2"
Slow_MeanESC2 <- data.frame(log2(assays(ESCobj1)$counts[, 4]), Proliferation)
colnames(Slow_MeanESC2) <- c("MeanExpression", "Proliferation")
Proliferation <- "MediumESC1"
Medium_MeanESC1 <- data.frame(log2(assays(ESCobj1)$counts[, 2]), Proliferation)
colnames(Medium_MeanESC1) <- c("MeanExpression", "Proliferation")
Proliferation <- "MediumESC2"
Medium_MeanESC2 <- data.frame(log2(assays(ESCobj1)$counts[, 5]), Proliferation)
colnames(Medium_MeanESC2) <- c("MeanExpression", "Proliferation")
Proliferation <- "FastESC1"
Fast_MeanESC1 <- data.frame(log2(assays(ESCobj1)$counts[, 3]), Proliferation)
colnames(Fast_MeanESC1) <- c("MeanExpression", "Proliferation")
Proliferation <- "FastESC2"
Fast_MeanESC2 <- data.frame(log2(assays(ESCobj1)$counts[, 6]), Proliferation)
colnames(Fast_MeanESC2) <- c("MeanExpression", "Proliferation")
ESCdf1 <- rbind(Slow_MeanESC1, Slow_MeanESC2, Medium_MeanESC1, Medium_MeanESC2, Fast_MeanESC1, Fast_MeanESC2)
ESCdf1 <- data.frame(ESCdf1)

plot_explevelsESC1 <- ggplot(ESCdf1, aes(x = ESCdf1[, 1], group = ESCdf1[, 2], color = ESCdf1[, 2])) + geom_density()
plot_explevelsESC1 <- plot_explevelsESC1 + xlab("Mean Expression (log2CPM)") + theme_bw() + theme(legend.title = element_blank())


#FIB

Proliferation <- "SlowFIB1"
Slow_MeanFIB1 <- data.frame(log2(assays(FIBobj1)$counts[, 1]), Proliferation)
colnames(Slow_MeanFIB1) <- c("MeanExpression", "Proliferation")
Proliferation <- "SlowFIB2"
Slow_MeanFIB2 <- data.frame(log2(assays(FIBobj1)$counts[, 4]), Proliferation)
colnames(Slow_MeanFIB2) <- c("MeanExpression", "Proliferation")
Proliferation <- "MediumFIB1"
Medium_MeanFIB1 <- data.frame(log2(assays(FIBobj1)$counts[, 2]), Proliferation)
colnames(Medium_MeanFIB1) <- c("MeanExpression", "Proliferation")
Proliferation <- "MediumFIB2"
Medium_MeanFIB2 <- data.frame(log2(assays(FIBobj1)$counts[, 5]), Proliferation)
colnames(Medium_MeanFIB2) <- c("MeanExpression", "Proliferation")
Proliferation <- "FastFIB1"
Fast_MeanFIB1 <- data.frame(log2(assays(FIBobj1)$counts[, 3]), Proliferation)
colnames(Fast_MeanFIB1) <- c("MeanExpression", "Proliferation")
Proliferation <- "FastFIB2"
Fast_MeanFIB2 <- data.frame(log2(assays(FIBobj1)$counts[, 6]), Proliferation)
colnames(Fast_MeanFIB2) <- c("MeanExpression", "Proliferation")
FIBdf1 <- rbind(Slow_MeanFIB1, Slow_MeanFIB2, Medium_MeanFIB1, Medium_MeanFIB2, Fast_MeanFIB1, Fast_MeanFIB2)
FIBdf1 <- data.frame(FIBdf1)

plot_explevelsFIB1 <- ggplot(FIBdf1, aes(x = FIBdf1[, 1], group = FIBdf1[, 2], color = FIBdf1[, 2])) + geom_density()
plot_explevelsFIB1 <- plot_explevelsFIB1 + xlab("Mean Expression (log2CPM)") + theme_bw() + theme(legend.title = element_blank())

```

We filter out low expressed genes in at least one of the replicates (cutoff: 0.5)

```{r}
ESCobj1 <- ESCobj1[rowMeans(assays(ESCobj1)$counts[, c(1,3)]) >= 0.5, ]
ESCobj1 <- ESCobj1[rowMeans(assays(ESCobj1)$counts[, c(4,6)]) >= 0.5, ]
FIBobj1 <- FIBobj1[rowMeans(assays(FIBobj1)$counts[, c(1,3)]) >= 0.5, ]
FIBobj1 <- FIBobj1[rowMeans(assays(FIBobj1)$counts[, c(4,6)]) >= 0.5, ]

#FIB
Slow_MeanFIB <- rowMeans(log2(assays(FIBobj1)$counts[, c(1, 4)]))
Proliferation <- "SlowFIB"
Slow_MeanFIB <- data.frame(Slow_MeanFIB, Proliferation)
colnames(Slow_MeanFIB) <- c("MeanExpression", "Proliferation")
Medium_MeanFIB <- rowMeans(log2(assays(FIBobj1)$counts[, c(2, 5)]))
Proliferation <- "MediumFIB"
Medium_MeanFIB <- data.frame(Medium_MeanFIB, Proliferation)
colnames(Medium_MeanFIB) <- c("MeanExpression", "Proliferation")
Fast_MeanFIB <- rowMeans(log2(assays(FIBobj1)$counts[, c(3, 6)]))
Proliferation <- "FastFIB"
Fast_MeanFIB <- data.frame(Fast_MeanFIB, Proliferation)
colnames(Fast_MeanFIB) <- c("MeanExpression", "Proliferation")
FIBdf <- rbind(Slow_MeanFIB, Medium_MeanFIB, Fast_MeanFIB)
colnames(FIBdf) <- c("MeanExpression", "Proliferation")
FIBdf <- data.frame(FIBdf)
plot_explevelsFIB <- ggplot(FIBdf, aes(x = FIBdf[, 1], group = FIBdf[, 2], color = FIBdf[, 2])) + geom_density()
plot_explevelsFIB <- plot_explevelsFIB + xlab("Mean Expression (log2CPM)") + theme_bw() + theme(legend.title = element_blank()) + xlim(c(-15, 15))
plot_explevelsFIB

#ESC
Slow_MeanESC <- rowMeans(log2(assays(ESCobj1)$counts[, c(1, 4)]))
Proliferation <- "SlowESC"
Slow_MeanESC <- data.frame(Slow_MeanESC, Proliferation)
colnames(Slow_MeanESC) <- c("MeanExpression", "Proliferation")
Medium_MeanESC <- rowMeans(log2(assays(ESCobj1)$counts[, c(2, 5)]))
Proliferation <- "MediumESC"
Medium_MeanESC <- data.frame(Medium_MeanESC, Proliferation)
colnames(Medium_MeanESC) <- c("MeanExpression", "Proliferation")
Fast_MeanESC <- rowMeans(log2(assays(ESCobj1)$counts[, c(3, 6)]))
Proliferation <- "FastESC"
Fast_MeanESC <- data.frame(Fast_MeanESC, Proliferation)
colnames(Fast_MeanESC) <- c("MeanExpression", "Proliferation")
ESCdf <- rbind(Slow_MeanESC, Medium_MeanESC, Fast_MeanESC)
colnames(ESCdf) <- c("MeanExpression", "Proliferation")
ESCdf <- data.frame(ESCdf)
plot_explevelsESC <- ggplot(ESCdf, aes(x = ESCdf[, 1], group = ESCdf[, 2], color = ESCdf[, 2])) + geom_density()
plot_explevelsESC <- plot_explevelsESC + xlab("Mean Expression (log2CPM)") + theme_bw() + theme(legend.title = element_blank()) + xlim(c(-15, 15))
plot_explevelsESC

```

```{r}

#ESC

Proliferation <- "SlowESC1"
Slow_MeanESC1 <- data.frame(log2(assays(ESCobj1)$counts[, 1]), Proliferation)
colnames(Slow_MeanESC1) <- c("MeanExpression", "Proliferation")
Proliferation <- "SlowESC2"
Slow_MeanESC2 <- data.frame(log2(assays(ESCobj1)$counts[, 4]), Proliferation)
colnames(Slow_MeanESC2) <- c("MeanExpression", "Proliferation")
Proliferation <- "MediumESC1"
Medium_MeanESC1 <- data.frame(log2(assays(ESCobj1)$counts[, 2]), Proliferation)
colnames(Medium_MeanESC1) <- c("MeanExpression", "Proliferation")
Proliferation <- "MediumESC2"
Medium_MeanESC2 <- data.frame(log2(assays(ESCobj1)$counts[, 5]), Proliferation)
colnames(Medium_MeanESC2) <- c("MeanExpression", "Proliferation")
Proliferation <- "FastESC1"
Fast_MeanESC1 <- data.frame(log2(assays(ESCobj1)$counts[, 3]), Proliferation)
colnames(Fast_MeanESC1) <- c("MeanExpression", "Proliferation")
Proliferation <- "FastESC2"
Fast_MeanESC2 <- data.frame(log2(assays(ESCobj1)$counts[, 6]), Proliferation)
colnames(Fast_MeanESC2) <- c("MeanExpression", "Proliferation")
ESCdf1 <- rbind(Slow_MeanESC1, Slow_MeanESC2, Medium_MeanESC1, Medium_MeanESC2, Fast_MeanESC1, Fast_MeanESC2)
ESCdf1 <- data.frame(ESCdf1)

plot_explevelsESC1 <- ggplot(ESCdf1, aes(x = ESCdf1[, 1], group = ESCdf1[, 2], color = ESCdf1[, 2])) + geom_density()
plot_explevelsESC1 <- plot_explevelsESC1 + xlab("Mean Expression (log2CPM)") + theme_bw() + theme(legend.title = element_blank()) + xlim(c(-15, 15))
plot_explevelsESC1


#FIB

Proliferation <- "SlowFIB1"
Slow_MeanFIB1 <- data.frame(log2(assays(FIBobj1)$counts[, 1]), Proliferation)
colnames(Slow_MeanFIB1) <- c("MeanExpression", "Proliferation")
Proliferation <- "SlowFIB2"
Slow_MeanFIB2 <- data.frame(log2(assays(FIBobj1)$counts[, 4]), Proliferation)
colnames(Slow_MeanFIB2) <- c("MeanExpression", "Proliferation")
Proliferation <- "MediumFIB1"
Medium_MeanFIB1 <- data.frame(log2(assays(FIBobj1)$counts[, 2]), Proliferation)
colnames(Medium_MeanFIB1) <- c("MeanExpression", "Proliferation")
Proliferation <- "MediumFIB2"
Medium_MeanFIB2 <- data.frame(log2(assays(FIBobj1)$counts[, 5]), Proliferation)
colnames(Medium_MeanFIB2) <- c("MeanExpression", "Proliferation")
Proliferation <- "FastFIB1"
Fast_MeanFIB1 <- data.frame(log2(assays(FIBobj1)$counts[, 3]), Proliferation)
colnames(Fast_MeanFIB1) <- c("MeanExpression", "Proliferation")
Proliferation <- "FastFIB2"
Fast_MeanFIB2 <- data.frame(log2(assays(FIBobj1)$counts[, 6]), Proliferation)
colnames(Fast_MeanFIB2) <- c("MeanExpression", "Proliferation")
FIBdf1 <- rbind(Slow_MeanFIB1, Slow_MeanFIB2, Medium_MeanFIB1, Medium_MeanFIB2, Fast_MeanFIB1, Fast_MeanFIB2)
FIBdf1 <- data.frame(FIBdf1)

plot_explevelsFIB1 <- ggplot(FIBdf1, aes(x = FIBdf1[, 1], group = FIBdf1[, 2], color = FIBdf1[, 2])) + geom_density()
plot_explevelsFIB1 <- plot_explevelsFIB1 + xlab("Mean Expression (log2CPM)") + theme_bw() + theme(legend.title = element_blank()) + xlim(c(-15, 15))
plot_explevelsFIB1
```

**Fold change distributions**

```{r}

#ESC
FC_ESC1 <- log2(assays(ESCobj1)$counts[ ,3]) - log2(assays(ESCobj1)$counts[ ,1])
Replicate <- "Rep1"
FC_ESC1 <- data.frame(FC_ESC1, Replicate)
colnames(FC_ESC1) <- c("FoldChange", "Replicate")
FC_ESC2 <- log2(assays(ESCobj1)$counts[ ,6]) - log2(assays(ESCobj1)$counts[ ,4])
Replicate <- "Rep2"
FC_ESC2 <- data.frame(FC_ESC2, Replicate)
colnames(FC_ESC2) <- c("FoldChange", "Replicate")
FC_ESCdf <- rbind(FC_ESC1, FC_ESC2)
FC_ESCdf <- data.frame(FC_ESCdf)

plot_FoldChangeESC1 <- ggplot(FC_ESCdf, aes(x = FC_ESCdf[, 1], group = FC_ESCdf[, 2], color = FC_ESCdf[, 2])) + geom_density()
plot_FoldChangeESC1 <- plot_FoldChangeESC1 + xlab("log2 FC (Fast/slow)") + theme_bw() + theme(legend.title = element_blank()) + xlim(c(-10, 10))
plot_FoldChangeESC1



#FIB
FC_FIB1 <- log2(assays(FIBobj1)$counts[ ,3]) - log2(assays(FIBobj1)$counts[ ,1])
Replicate <- "Rep1"
FC_FIB1 <- data.frame(FC_FIB1, Replicate)
colnames(FC_FIB1) <- c("FoldChange", "Replicate")
FC_FIB2 <- log2(assays(FIBobj1)$counts[ ,6]) - log2(assays(FIBobj1)$counts[ ,4])
Replicate <- "Rep2"
FC_FIB2 <- data.frame(FC_FIB2, Replicate)
colnames(FC_FIB2) <- c("FoldChange", "Replicate")
FC_FIBdf <- rbind(FC_FIB1, FC_FIB2)
FC_FIBdf <- data.frame(FC_FIBdf)

plot_FoldChangeFIB1 <- ggplot(FC_FIBdf, aes(x = FC_FIBdf[, 1], group = FC_FIBdf[, 2], color = FC_FIBdf[, 2])) + geom_density()
plot_FoldChangeFIB1 <- plot_FoldChangeFIB1 + xlab("log2 FC (Fast/slow)") + theme_bw() + theme(legend.title = element_blank()) + xlim(c(-10, 10))
plot_FoldChangeFIB1


```

As we are only interested in the differences between slow and fast populations, we will drop the medium proliferation column 

```{r}
#ESCobj1 <- ESCobj1[, c(1, 3, 4, 6)]
#FIBobj1 <- FIBobj1[, c(1, 3, 4, 6)]
```

#DEA 

1. Build the design matrix: 

```{r}
design_matrixESC <- model.matrix(~ProliferationIndex, data = colData(ESCobj1))
design_matrixFIB <- model.matrix(~ProliferationIndex, data = colData(FIBobj1))
```

2, 3. Fit linear regression model and calculate moderate t-statistics:

!! Important: if we don't substitute 0 values for 0.0001 in the counts matrix we will have an error: Partial NA coefficients for XXX probe(s). 

```{r}
fitESC <- lmFit(log2(assays(ESCobj1)$counts), design_matrixESC)
fitESC <- eBayes(fitESC)

fitFIB <- lmFit(log2(assays(FIBobj1)$counts), design_matrixFIB)
fitFIB <- eBayes(fitFIB)

resFIB <- decideTests(fitFIB, p.value = 0.01)
summary(resFIB)
ttFIB <- topTable(fitFIB, coef = 2, n = Inf)
head(ttFIB)

resESC <- decideTests(fitESC, p.value = 0.01)
summary(resESC)
ttESC <- topTable(fitESC, coef = 2, n = Inf)
head(ttESC)

```

**Volcano plot**

```{r}
ttFIB$log10.P.Val <- log10(ttFIB$P.Value) * (-1)
ttFIB$significance <- ttFIB$log10.P.Val >= -1 * log10(0.01)
VolcanoFIB <- ggplot(ttFIB, aes(logFC, log10.P.Val, color = significance)) +
  geom_point() + 
  theme_bw() + 
  scale_y_continuous(limits = c(0, 10), expand = c(0,0)) +
  scale_x_continuous(breaks = c(-10, -5, 0, 5, 10)) +
  scale_color_manual(values = c("#e88c8c", "#b62525")) +
  labs(x = "log2 (fold-change)", y = "-log10 (p-value)")
VolcanoFIB

ttESC$log10.P.Val <- log10(ttESC$P.Value) * (-1)
ttESC$significance <- ttESC$log10.P.Val >= -1 * log10(0.01)
VolcanoESC <- ggplot(ttESC, aes(logFC, log10.P.Val, color = significance)) +
  geom_point() + 
  theme_bw() + 
  scale_y_continuous(limits = c(0, 10), expand = c(0,0)) +
  scale_x_continuous(breaks = c(-10, -5, 0, 5, 10)) +
  scale_color_manual(values = c("#e88c8c", "#b62525")) +
  labs(x = "log2 (fold-change)", y = "-log10 (p-value)")
VolcanoESC
```

If we trust the volcano plots, we should take into account "top" left & right. 

```{r}
#FIB 

ttFIB1 <- ttFIB[ttFIB$logFC > 1 & ttFIB$significance == TRUE || ttFIB$logFC < -1 & ttFIB$significance == TRUE, ]
dim(ttFIB)
FIB2GOrilla <- substr(row.names(ttFIB), 1, 18)
write.table(substr(rowData(FIBobj1)$ENS_id, 1, 18), quote = FALSE, sep = "\t", row.names = FALSE, file = "TargetFIB2GOrilla.tsv")
write.table(substr(rowData(FIBobj1)$ENS_id, 1, 18), quote = FALSE, sep = "\t", row.names = FALSE, file = "BackgroundFIB2GOrilla.tsv")
```





#EXPLORATORY ANALYSIS

##PCA 
(Let's see how our samples cluster)
To apply R function prcomp we need the following data format (columns: samples, rows: attributes/genes). In ESC: PC1 seems to separate by proliferation state and PC3 separates by replicate. 

```{r}
library(ggfortify)
ESC2PCA <- t(log2(assays(ESCobj1)$counts))
PCA_ESC <- prcomp(ESC2PCA)
autoplot(prcomp(ESC2PCA, center = TRUE), x = 3, y = 2, data = ESC2PCA, label = TRUE)
```

