
Load packages.

```{r}
require(ggplot2)
require(reshape2)
require(gtools)
```

Load RNA counts files from both experiments and uniformize gene ID. 
FIB2016 & ESC2016: first sequencing experiment. 
FIB2016 & ESC2016: last sequencing experiment, only showing the ones from CFSE experiment.

```{r}
FIB2016 <- read.csv("FIBBehavGroups.tsv", sep = "\t", header = TRUE)
FIB2016$X <- substr(FIB2016$X, 1, 18)
ESC2016 <- read.csv("ESCBehavGroups.tsv", sep = "\t", header = TRUE)
ESC2016$X <- substr(ESC2016$X, 1, 18)
```

As we want to plot specific genes, we extract their ENSEMBL ID from the whole dataframe. In this case Tars - threonyl-tRNA synthetase - ENS: ENSMUSG00000022241, Pmaip1 - phorbol-12-myristate-13-acetate-induced protein 1 - ENS: ENSMUSG00000024521, Rpa1rsf21 - tumor necrosis factor receptor superfamily, member 21 - ENS: ENSMUSG00000023915). 

```{r}
Columns2Keep2016S1 <- c("S1_TPM", "S1_TPM_95CI_low", "S1_TPM_95CI_high")
Columns2Keep2016F1 <- c("F1_TPM", "F1_TPM_95CI_low", "F1_TPM_95CI_high") 
Columns2Keep2016S2 <- c("S2_TPM", "S2_TPM_95CI_low", "S2_TPM_95CI_high") 
Columns2Keep2016F2 <- c("F2_TPM", "F2_TPM_95CI_low", "F2_TPM_95CI_high")

NewColNames <- c("median", "lowerCI", "higherCI")

PmaipFIB16S1 <- FIB2016[FIB2016$X == "ENSMUSG00000024521", Columns2Keep2016S1]
PmaipFIB16F1 <- FIB2016[FIB2016$X == "ENSMUSG00000024521", Columns2Keep2016F1]
PmaipFIB16S2 <- FIB2016[FIB2016$X == "ENSMUSG00000024521", Columns2Keep2016S2]
PmaipFIB16F2 <- FIB2016[FIB2016$X == "ENSMUSG00000024521", Columns2Keep2016F2]
colnames(PmaipFIB16S1) <- NewColNames
colnames(PmaipFIB16F1) <- NewColNames
colnames(PmaipFIB16S2) <- NewColNames
colnames(PmaipFIB16F2) <- NewColNames

PmaipESC16S1 <- ESC2016[ESC2016$X == "ENSMUSG00000024521", Columns2Keep2016S1]
PmaipESC16F1 <- ESC2016[ESC2016$X == "ENSMUSG00000024521", Columns2Keep2016F1]
PmaipESC16S2 <- ESC2016[ESC2016$X == "ENSMUSG00000024521", Columns2Keep2016S2]
PmaipESC16F2 <- ESC2016[ESC2016$X == "ENSMUSG00000024521", Columns2Keep2016F2]
colnames(PmaipESC16S1) <- NewColNames
colnames(PmaipESC16F1) <- NewColNames
colnames(PmaipESC16S2) <- NewColNames
colnames(PmaipESC16F2) <- NewColNames

Pmaip <- smartbind(PmaipFIB16S1, PmaipFIB16F1, PmaipFIB16S2, PmaipFIB16F2, PmaipESC16S1, PmaipESC16F1, PmaipESC16S2, PmaipESC16F2)

ProlifIndex <- rep(c("Slow", "Fast"), 4)
CellType <- rep(c(rep("FIB", 4), rep("ESC", 4)))
Replicate <- rep(c(rep(1, 2), rep(2, 2)), 2)

Pmaip$ProlifIndex <- ProlifIndex
Pmaip$CellType <- CellType
Pmaip$Replicate <- Replicate 
Pmaip$all <- paste(CellType, Replicate)
```

```{r}
PmaipPlot <- ggplot(Pmaip, aes(x = factor(Pmaip$ProlifIndex, levels = rev(levels(factor(Pmaip$ProlifIndex)))), y = log2(Pmaip$median), group = Pmaip$all, color = Pmaip$CellType)) + geom_line(aes(linetype = factor(Pmaip$Replicate))) + geom_point() + geom_errorbar(width = 0.05, aes(ymin = log2(Pmaip$lowerCI), ymax = log2(Pmaip$higherCI))) + scale_color_manual(values = c("#903B6F", "#538135")) + ylab("log2(TPM)") + xlab("") + theme_bw() + theme(legend.title = element_blank(), plot.title = element_text(hjust = 0.5)) + ggtitle("Pmaip1")
PmaipPlot
```

```{r}
Columns2Keep2016S1 <- c("S1_TPM", "S1_TPM_95CI_low", "S1_TPM_95CI_high")
Columns2Keep2016F1 <- c("F1_TPM", "F1_TPM_95CI_low", "F1_TPM_95CI_high") 
Columns2Keep2016S2 <- c("S2_TPM", "S2_TPM_95CI_low", "S2_TPM_95CI_high") 
Columns2Keep2016F2 <- c("F2_TPM", "F2_TPM_95CI_low", "F2_TPM_95CI_high")

NewColNames <- c("median", "lowerCI", "higherCI")

TarsFIB16S1 <- FIB2016[FIB2016$X == "ENSMUSG00000022241", Columns2Keep2016S1]
TarsFIB16F1 <- FIB2016[FIB2016$X == "ENSMUSG00000022241", Columns2Keep2016F1]
TarsFIB16S2 <- FIB2016[FIB2016$X == "ENSMUSG00000022241", Columns2Keep2016S2]
TarsFIB16F2 <- FIB2016[FIB2016$X == "ENSMUSG00000022241", Columns2Keep2016F2]
colnames(TarsFIB16S1) <- NewColNames
colnames(TarsFIB16F1) <- NewColNames
colnames(TarsFIB16S2) <- NewColNames
colnames(TarsFIB16F2) <- NewColNames

TarsESC16S1 <- ESC2016[ESC2016$X == "ENSMUSG00000022241", Columns2Keep2016S1]
TarsESC16F1 <- ESC2016[ESC2016$X == "ENSMUSG00000022241", Columns2Keep2016F1]
TarsESC16S2 <- ESC2016[ESC2016$X == "ENSMUSG00000022241", Columns2Keep2016S2]
TarsESC16F2 <- ESC2016[ESC2016$X == "ENSMUSG00000022241", Columns2Keep2016F2]
colnames(TarsESC16S1) <- NewColNames
colnames(TarsESC16F1) <- NewColNames
colnames(TarsESC16S2) <- NewColNames
colnames(TarsESC16F2) <- NewColNames

Tars <- smartbind(TarsFIB16S1, TarsFIB16F1, TarsFIB16S2, TarsFIB16F2, TarsESC16S1, TarsESC16F1, TarsESC16S2, TarsESC16F2)

ProlifIndex <- rep(c("Slow", "Fast"), 4)
CellType <- rep(c(rep("FIB", 4), rep("ESC", 4)))
Replicate <- rep(c(rep(1, 2), rep(2, 2)), 2)

Tars$ProlifIndex <- ProlifIndex
Tars$CellType <- CellType
Tars$Replicate <- Replicate 
Tars$all <- paste(CellType, Replicate)
```

```{r}
TarsPlot <- ggplot(Tars, aes(x = factor(Tars$ProlifIndex, levels = rev(levels(factor(Tars$ProlifIndex)))), y = log2(Tars$median), group = Tars$all, color = Tars$CellType)) + geom_line(aes(linetype = factor(Tars$Replicate))) + geom_point() + geom_errorbar(width = 0.05, aes(ymin = log2(Tars$lowerCI), ymax = log2(Tars$higherCI))) + scale_color_manual(values = c("#903B6F", "#538135")) + ylab("log2(TPM)") + xlab("") + theme_bw() + theme(legend.title = element_blank(), plot.title = element_text(hjust = 0.5)) + ggtitle("Tars")
TarsPlot 
```


```{r}
Columns2Keep2016S1 <- c("S1_TPM", "S1_TPM_95CI_low", "S1_TPM_95CI_high")
Columns2Keep2016F1 <- c("F1_TPM", "F1_TPM_95CI_low", "F1_TPM_95CI_high") 
Columns2Keep2016S2 <- c("S2_TPM", "S2_TPM_95CI_low", "S2_TPM_95CI_high") 
Columns2Keep2016F2 <- c("F2_TPM", "F2_TPM_95CI_low", "F2_TPM_95CI_high")

NewColNames <- c("median", "lowerCI", "higherCI")

Tnfrsf21FIB16S1 <- FIB2016[FIB2016$X == "ENSMUSG00000023915", Columns2Keep2016S1]
Tnfrsf21FIB16F1 <- FIB2016[FIB2016$X == "ENSMUSG00000023915", Columns2Keep2016F1]
Tnfrsf21FIB16S2 <- FIB2016[FIB2016$X == "ENSMUSG00000023915", Columns2Keep2016S2]
Tnfrsf21FIB16F2 <- FIB2016[FIB2016$X == "ENSMUSG00000023915", Columns2Keep2016F2]
colnames(Tnfrsf21FIB16S1) <- NewColNames
colnames(Tnfrsf21FIB16F1) <- NewColNames
colnames(Tnfrsf21FIB16S2) <- NewColNames
colnames(Tnfrsf21FIB16F2) <- NewColNames

Tnfrsf21ESC16S1 <- ESC2016[ESC2016$X == "ENSMUSG00000023915", Columns2Keep2016S1]
Tnfrsf21ESC16F1 <- ESC2016[ESC2016$X == "ENSMUSG00000023915", Columns2Keep2016F1]
Tnfrsf21ESC16S2 <- ESC2016[ESC2016$X == "ENSMUSG00000023915", Columns2Keep2016S2]
Tnfrsf21ESC16F2 <- ESC2016[ESC2016$X == "ENSMUSG00000023915", Columns2Keep2016F2]
colnames(Tnfrsf21ESC16S1) <- NewColNames
colnames(Tnfrsf21ESC16F1) <- NewColNames
colnames(Tnfrsf21ESC16S2) <- NewColNames
colnames(Tnfrsf21ESC16F2) <- NewColNames

Tnfrsf21 <- smartbind(Tnfrsf21FIB16S1, Tnfrsf21FIB16F1, Tnfrsf21FIB16S2, Tnfrsf21FIB16F2, Tnfrsf21ESC16S1, Tnfrsf21ESC16F1, Tnfrsf21ESC16S2, Tnfrsf21ESC16F2)

ProlifIndex <- rep(c("Slow", "Fast"), 4)
CellType <- rep(c(rep("FIB", 4), rep("ESC", 4)))
Replicate <- rep(c(rep(1, 2), rep(2, 2)), 2)

Tnfrsf21$ProlifIndex <- ProlifIndex
Tnfrsf21$CellType <- CellType
Tnfrsf21$Replicate <- Replicate 
Tnfrsf21$all <- paste(CellType, Replicate)
```

```{r}
Tnfrsf21Plot <- ggplot(Tnfrsf21, aes(x = factor(Tnfrsf21$ProlifIndex, levels = rev(levels(factor(Tnfrsf21$ProlifIndex)))), y = log2(Tnfrsf21$median), group = Tnfrsf21$all, color = Tnfrsf21$CellType)) + geom_line(aes(linetype = factor(Tnfrsf21$Replicate))) + geom_point() + geom_errorbar(width = 0.05, aes(ymin = log2(Tnfrsf21$lowerCI), ymax = log2(Tnfrsf21$higherCI))) + scale_color_manual(values = c("#903B6F", "#538135")) + ylab("log2(TPM)") + xlab("") + theme_bw() + theme(legend.title = element_blank(), plot.title = element_text(hjust = 0.5)) + ggtitle("Tnfrsf21")
Tnfrsf21Plot
```