
Script to generate correlation plots between replicates. 

Load packages. 

```{r}
require(ggplot2)
require(ggpubr)
```

Load FIB files; replace expression values lower than 0.001 with 0.001 and calculate log2 TPM. 

```{r}
FIB <- read.table("FIB_TMRESep2018.tsv", sep = "\t", header = TRUE, row.names = 1)
FIB[FIB < 0.001] <- 0.001
FIB <- log2(FIB)
```

Create 2 dataframes, one for each population (low TMRE and high TMRE)

```{r}
highFIB <- FIB[, c(grep("high_median", names(FIB), value=TRUE))]
lowFIB <- FIB[, c(grep("low_median", names(FIB), value=TRUE))]
```

Load ESC files; replace expression values lower than 0.001 with 0.001 and calculate log2 TPM. 

```{r}
ESC <- read.table("ES_TMRESep2018.tsv", sep = "\t", header = TRUE, row.names = 1)
ESC[ESC < 0.001] <- 0.001
ESC <- log2(ESC)
```

Create 2 dataframes, one for each population (low TMRE and high TMRE)

```{r}
highESC <- ESC[, c(grep("high_median", names(ESC), value=TRUE))]
lowESC <- ESC[, c(grep("low_median", names(ESC), value=TRUE))]
```

We want to plot compare each replicate to the others.

```{r}
Combinations <- combn(x = c(1, 2, 3, 4), m = 2) #To use the apply function we need a matrix with the pairwise combinations of all the replicates. 
```

Plot each pair of replicates. 

```{r}
#ESC Low TMRE population 
ESC_LowPlots <- apply(Combinations, 2, function(i) ggplot(lowESC, aes(x = lowESC[, i[1]], y = lowESC[, i[2]])) + geom_point() + xlab(paste("log2(TPM) Replicate", i[1])) + ylab(paste("log2(TPM) Replicate", i[2])) + ggtitle("Low ESC") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + stat_cor(method = "pearson", label.x = 1))

lapply(c(1:length(ESC_LowPlots)), function(i) ggsave(filename = paste("Cor_LowESC", i, ".pdf"), plot = ESC_LowPlots[[i]], device = "pdf")) #save files 

#ESC High TMRE population                  
ESC_HighPlots <- apply(Combinations, 2, function(i) ggplot(highESC, aes(x = highESC[, i[1]], y = highESC[, i[2]])) + geom_point() + xlab(paste("log2(TPM) Replicate", i[1])) + ylab(paste("log2(TPM) Replicate", i[2])) + ggtitle("High ESC") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + stat_cor(method = "pearson", label.x = 1))

lapply(c(1:length(ESC_HighPlots)), function(i) ggsave(filename = paste("Cor_HighESC", i, ".pdf"), plot = ESC_HighPlots[[i]], device = "pdf")) #save files

#FIB Low TMRE population 
FIB_LowPlots <- apply(Combinations, 2, function(i) ggplot(lowFIB, aes(x = lowFIB[, i[1]], y = lowFIB[, i[2]])) + geom_point() + xlab(paste("log2(TPM) Replicate", i[1])) + ylab(paste("log2(TPM) Replicate", i[2])) + ggtitle("Low FIB") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + stat_cor(method = "pearson", label.x = 1))

lapply(c(1:length(FIB_LowPlots)), function(i) ggsave(filename = paste("Cor_LowFIB", i, ".pdf"), plot = FIB_LowPlots[[i]], device = "pdf")) #save files
```

We need to create a new combinatory matrix because we only have 3 replicates of FIB high TMRE. (In the other cases we had 4 reps).  

```{r}
Combinations <- combn(x = c(1, 2, 3), m = 2)

#FIB high TMRE population 
FIB_HighPlots <- apply(Combinations, 2, function(i) ggplot(highFIB, aes(x = highFIB[, i[1]], y = highFIB[, i[2]])) + geom_point() + xlab(paste("log2(TPM) Replicate", i[1])) + ylab(paste("log2(TPM) Replicate", i[2])) + ggtitle("High FIB") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + stat_cor(method = "pearson", label.x = 1))

lapply(c(1:length(FIB_HighPlots)), function(i) ggsave(filename = paste("Cor_HighFIB", i, ".pdf"), plot = FIB_HighPlots[[i]], device = "pdf"))
```

